---
title: "Redraft Summaries"
output:
  pdf_document: default
  html_document: default
---


```{r, include=FALSE}
library(ggpubr)
library(rvest)
library(ggplot2)
library(ggthemes)
library(dplyr)
library(formattable)

as.df = read.csv("allstardf.csv")
as.stats2019 = as.df %>% filter(Yr == 2019) %>% arrange(desc(allstar.pred))
as.stats2018 = as.df %>% filter(Yr == 2018) %>% arrange(desc(allstar.pred))
as.stats2017 = as.df %>% filter(Yr == 2017) %>% arrange(desc(allstar.pred))
as.stats2016 = as.df %>% filter(Yr == 2016) %>% arrange(desc(allstar.pred))
as.stats2015 = as.df %>% filter(Yr == 2015) %>% arrange(desc(allstar.pred))
as.stats2014 = as.df %>% filter(Yr == 2014) %>% arrange(desc(allstar.pred))
as.stats2013 = as.df %>% filter(Yr == 2013) %>% arrange(desc(allstar.pred))
as.stats2012 = as.df %>% filter(Yr == 2012) %>% arrange(desc(allstar.pred))
as.stats2011 = as.df %>% filter(Yr == 2011) %>% arrange(desc(allstar.pred))
as.stats2010 = as.df %>% filter(Yr == 2010) %>% arrange(desc(allstar.pred))

as.stats2009 = as.df %>% filter(Yr == 2009) %>% arrange(desc(allstar.pred))
as.stats2008 = as.df %>% filter(Yr == 2008) %>% arrange(desc(allstar.pred))
as.stats2007 = as.df %>% filter(Yr == 2007) %>% arrange(desc(allstar.pred))
as.stats2006 = as.df %>% filter(Yr == 2006) %>% arrange(desc(allstar.pred))
as.stats2005 = as.df %>% filter(Yr == 2005) %>% arrange(desc(allstar.pred))
as.stats2004 = as.df %>% filter(Yr == 2004) %>% arrange(desc(allstar.pred))
as.stats2003 = as.df %>% filter(Yr == 2003) %>% arrange(desc(allstar.pred))
as.stats2002 = as.df %>% filter(Yr == 2002) %>% arrange(desc(allstar.pred))
as.stats2001 = as.df %>% filter(Yr == 2001) %>% arrange(desc(allstar.pred))
as.stats2000 = as.df %>% filter(Yr == 2000) %>% arrange(desc(allstar.pred))

as.stats1999 = as.df %>% filter(Yr == 1999) %>% arrange(desc(allstar.pred))
as.stats1998 = as.df %>% filter(Yr == 1998) %>% arrange(desc(allstar.pred))
as.stats1997 = as.df %>% filter(Yr == 1997) %>% arrange(desc(allstar.pred))
as.stats1996 = as.df %>% filter(Yr == 1996) %>% arrange(desc(allstar.pred))
as.stats1995 = as.df %>% filter(Yr == 1995) %>% arrange(desc(allstar.pred))



dat = read.csv("currentplayers.csv")
current.pl = dat$Player

```


  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2019 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2019 = sum(as.stats2019$Player %in% current.pl)/nrow(as.stats2019)
print(perc.2019)

```

```{r, echo = F}

head(as.stats2019, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2018 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2018 = sum(as.stats2018$Player %in% current.pl)/nrow(as.stats2018)
print(perc.2018)

```

```{r, echo = F}

head(as.stats2018, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2017 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2017 = sum(as.stats2017$Player %in% current.pl)/nrow(as.stats2017)
print(perc.2017)

```

```{r, echo = F}

head(as.stats2017, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2016 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2016 = sum(as.stats2016$Player %in% current.pl)/nrow(as.stats2016)
print(perc.2016)

```

```{r, echo = F}

head(as.stats2016, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2015 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2015 = sum(as.stats2015$Player %in% current.pl)/nrow(as.stats2015)
print(perc.2015)

```

```{r, echo = F}

head(as.stats2015, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2014 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2014 = sum(as.stats2014$Player %in% current.pl)/nrow(as.stats2014)
print(perc.2014)

```

```{r, echo = F}

head(as.stats2014, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2013 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2013 = sum(as.stats2013$Player %in% current.pl)/nrow(as.stats2013)
print(perc.2013)

```

```{r, echo = F}

head(as.stats2013, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2012 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2012 = sum(as.stats2012$Player %in% current.pl)/nrow(as.stats2012)
print(perc.2012)

```

```{r, echo = F}

head(as.stats2012, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2011 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2011 = sum(as.stats2011$Player %in% current.pl)/nrow(as.stats2011)
print(perc.2011)

```

```{r, echo = F}

head(as.stats2011, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2010 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2010 = sum(as.stats2010$Player %in% current.pl)/nrow(as.stats2010)
print(perc.2010)

```

```{r, echo = F}

head(as.stats2010, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```


## 2009 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2009 = sum(as.stats2009$Player %in% current.pl)/nrow(as.stats2009)
print(perc.2009)

```

```{r, echo = F}

head(as.stats2009, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2008 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2008 = sum(as.stats2008$Player %in% current.pl)/nrow(as.stats2008)
print(perc.2008)

```

```{r, echo = F}

head(as.stats2008, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2007 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2007 = sum(as.stats2007$Player %in% current.pl)/nrow(as.stats2007)
print(perc.2007)

```

```{r, echo = F}

head(as.stats2007, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2006 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2006 = sum(as.stats2006$Player %in% current.pl)/nrow(as.stats2006)
print(perc.2006)

```

```{r, echo = F}

head(as.stats2006, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2005 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2005 = sum(as.stats2005$Player %in% current.pl)/nrow(as.stats2005)
print(perc.2005)

```

```{r, echo = F}

head(as.stats2005, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2004 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2004 = sum(as.stats2004$Player %in% current.pl)/nrow(as.stats2004)
print(perc.2004)

```

```{r, echo = F}

head(as.stats2004, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2003 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2003 = sum(as.stats2003$Player %in% current.pl)/nrow(as.stats2003)
print(perc.2003)

```

```{r, echo = F}

head(as.stats2003, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2002 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2002 = sum(as.stats2002$Player %in% current.pl)/nrow(as.stats2002)
print(perc.2002)

```

```{r, echo = F}

head(as.stats2002, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2001 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2001 = sum(as.stats2001$Player %in% current.pl)/nrow(as.stats2001)
print(perc.2001)

```

```{r, echo = F}

head(as.stats2001, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 2000 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.2000 = sum(as.stats2000$Player %in% current.pl)/nrow(as.stats2000)
print(perc.2000)

```

```{r, echo = F}

head(as.stats2000, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```


## 1999 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.1999 = sum(as.stats1999$Player %in% current.pl)/nrow(as.stats1999)
print(perc.1999)

```

```{r, echo = F}

head(as.stats1999, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 1998 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.1998 = sum(as.stats1998$Player %in% current.pl)/nrow(as.stats1998)
print(perc.1998)

```

```{r, echo = F}

head(as.stats1998, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 1997 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.1997 = sum(as.stats1997$Player %in% current.pl)/nrow(as.stats1997)
print(perc.1997)

```

```{r, echo = F}

head(as.stats1997, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 1996 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.1996 = sum(as.stats1996$Player %in% current.pl)/nrow(as.stats1996)
print(perc.1996)

```

```{r, echo = F}

head(as.stats1996, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```

  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## 1995 Draft

Percent of players from this draft list who played in 2020:
```{r, echo = F}
perc.1995 = sum(as.stats1995$Player %in% current.pl)/nrow(as.stats1995)
print(perc.1995)

```

```{r, echo = F}

head(as.stats1995, 30) %>% select(Player, WS, VORP, allstar.pred, allstar)

```


  ```{r, results='asis', echo=FALSE}
cat("\\newpage")
```

## Cluster Analysis

This is a graph of the percentage of players from each draft class who are active. To make the process of choosing cutoffs for groups to model easier, we will use K-means clustering on these percentages and decide which number of groups is the most appropriate.

&nbsp;
&nbsp;

```{r, echo = F}
year = seq(1995, 2019, by=1)
percent = c(perc.1995, perc.1996, perc.1997, perc.1998, perc.1999,
            perc.2000, perc.2001, perc.2002, perc.2003, perc.2004,
            perc.2005, perc.2006, perc.2007, perc.2008, perc.2009,
            perc.2010, perc.2011, perc.2012, perc.2013, perc.2014,
            perc.2015, perc.2016, perc.2017, perc.2018, perc.2019)
perc.df = cbind.data.frame(year, percent)
ggplot(data = perc.df, aes(x = year, y = percent)) + geom_point() + theme_bw() + geom_bar(stat = "identity", width = I(1/12)) + scale_x_continuous("Draft Class") + scale_y_continuous("Percent in NBA (2020)")



```

```{r, echo = F}
# Clustering
set.seed(1)
kmeans_2 = kmeans(perc.df[2],centers=2, nstart = 10, iter.max = 10)
kmeans_3 = kmeans(perc.df[2],centers=3, nstart = 10, iter.max = 10)
kmeans_4 = kmeans(perc.df[2],centers=4, nstart = 10, iter.max = 10)
kmeans_5 = kmeans(perc.df[2],centers=5, nstart = 10, iter.max = 10)
perc.df1 = cbind.data.frame(perc.df, p2 = kmeans_2$cluster, p3 = kmeans_3$cluster, p4 = kmeans_4$cluster, p5 = kmeans_5$cluster)

pl1 = ggplot(data = perc.df1, aes(x = year, y = percent)) + geom_bar(stat = "identity", aes(fill = as.factor(p2)), width = I(1/8)) + theme_bw() + scale_x_continuous("Draft Class", breaks = seq(1995, 2015, by = 5)) + scale_y_continuous("Percent in NBA (2020)") + theme(legend.position = "none") + ggtitle("Split into Two Groups") + geom_vline(xintercept = 2010.5, linetype = "dashed", color = "grey30")

pl2 = ggplot(data = perc.df1, aes(x = year, y = percent)) + geom_bar(stat = "identity", aes(fill = as.factor(p3)), width = I(1/8)) + theme_bw() + scale_x_continuous("Draft Class", breaks = seq(1995, 2015, by = 5)) + scale_y_continuous("Percent in NBA (2020)") + theme(legend.position = "none") + ggtitle("Split into Three Groups") + geom_vline(xintercept = c(2014.5, 2007.5), linetype = "dashed", color = "grey30")

pl3 = ggplot(data = perc.df1, aes(x = year, y = percent)) + geom_bar(stat = "identity", aes(fill = as.factor(p4)), width = I(1/8)) + theme_bw() + scale_x_continuous("Draft Class", breaks = seq(1995, 2015, by = 5)) + scale_y_continuous("Percent in NBA (2020)") + theme(legend.position = "none") + ggtitle("Split into Four Groups") + geom_vline(xintercept = c(2016.5, 2010.5, 2005.5), linetype = "dashed", color = "grey30")

pl4 = ggplot(data = perc.df1, aes(x = year, y = percent)) + geom_bar(stat = "identity", aes(fill = as.factor(p5)), width = I(1/6)) + theme_bw() + scale_x_continuous("Draft Class", breaks = seq(1995, 2015, by = 5)) + scale_y_continuous("Percent in NBA (2020)") + theme(legend.position = "none") + ggtitle("Split into Five Groups") + geom_vline(xintercept = c(2016.5, 2010.5, 2005.5, 2013.5), linetype = "dashed", color = "grey30")

ggarrange(pl1, pl2, pl3, pl4, ncol = 2, nrow = 2)

```

&nbsp;
&nbsp;


Five Groups | Four Groups | Three Groups | Two Groups
------------- | ------------- | ------------- | -------------
Group 1: 1995-2005 | Group 1: 1995-2005 | Group 1: 1995-2007 | Group 1: 1995-2010 
Group 2: 2006-2010 | Group 2: 2006-2010 | Group 2: 2008-2014 | Group 2: 2011-2019
Group 3: 2011-2013 | Group 3: 2011-2016 | Group 3: 2015-2019 
Group 4: 2014-2016 | Group 4: 2016-2019
Group 5: 2017-2019 |
 
